---
title: "Twitter during electoral campaign: most discussed topics by italian parties"
author: "Simone Travaglini"
date: "2022-12-22"
output: html_document
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "C:\\Users\\trava\\OneDrive\\Documenti\\Capstone_TravagliniSimone\\script")
```

## INTRODUCTION:

On 21 July 2022 the president of the Republic **Sergio Mattarella** proclaimed the dissolution of parliament, following the resignation presented by prime minister Mario Draghi. early elections were called for 25 september: in those months, therefore, the parties began their electoral campaign.
Said that, this brief analysis aims to see which topics were most discussed by the main political actors and the candidates for the Chamber of Deputies and the Senate. in order to do so, I will use the twitter profiles, both personal and of the political parties of the main coalitions: **right coalition, left coalition, 5 star movement and Azione-Italia Viva**.

## METHODOLOGY:

As mentioned in the introduction, to do this I analysed the twitter profiles of Italian political actors. 
The first step in this analysis was to search for the various profiles and insert them, via my twitter profile, within 4 different lists, each concerning a coalition.
The lists were composed as follows:
1) right coalition: 80 members
2) left coalition: 70 members
3) m5s: 69 members
4) third pole: 35 members

The lists were created to make the work easier for me, and then import the various tweets divided by coalition.
Once this is done, the goal will be to create tables with tweets from 23 July until 24 September (the day before the elections) and extract hashtags from all tweets to see which are the most used in this period by each political group.
```{r, eval=FALSE}
library(rtweet)
library(tidyverse)
library(dplyr)


auth_setup_default()

#cdx list number 1602429027561750528-------
italian_cdx = lists_members(
  list_id = "1602429027561750528",
  owner_user = NULL,
  slug = NULL,
  cursor = "-1",
  token = NULL,
  retryonratelimit = TRUE,
  parse = TRUE,
  verbose = TRUE,
  
)

#csx list number 1602661051400654850------
italian_csx = lists_members(
  list_id = "1602661051400654850",
  owner_user = NULL,
  slug = NULL,
  cursor = "-1",
  token = NULL,
  retryonratelimit = TRUE,
  parse = TRUE,
  verbose = TRUE,
  
)

#terzo polo list number 1602680072506408960-------
italian_terzopolo = lists_members(
  list_id = "1602680072506408960",
  owner_user = NULL,
  slug = NULL,
  cursor = "-1",
  token = NULL,
  retryonratelimit = TRUE,
  parse = TRUE,
  verbose = TRUE,
  
)

#m5s list number 1602433071604801537---------
italian_m5s = lists_members(
  list_id = "1602433071604801537",
  owner_user = NULL,
  slug = NULL,
  cursor = "-1",
  token = NULL,
  retryonratelimit = TRUE,
  parse = TRUE,
  verbose = TRUE,
  
)
#lists are not completed, cause twitter dont let me finish (probably caused by a temporal block)
#i'll try tomorrow

##prove-----
# Create a string with the profile account

list_italian_cdx = c(italian_cdx$screen_name)
list_italian_csx = c(italian_csx$screen_name)
list_italian_m5s = c(italian_m5s$screen_name)
list_italian_terzopolo = c(italian_terzopolo$screen_name)

```


## SCRAPING OF TWEETS

After importing the profiles into the data frames, the first thing I did was to create lists containing only the screen_name for each coalition.

```{r, eval=FALSE}
library(rtweet)
library(tidyverse)
library(dplyr)

list_italian_cdx = c(italian_cdx$screen_name)
list_italian_csx = c(italian_csx$screen_name)
list_italian_m5s = c(italian_m5s$screen_name)
list_italian_terzopolo = c(italian_terzopolo$screen_name)

```

This was useful because I needed the ids to download the tweets of each politician.
The main problem in this process was setting up a filter, so that i could only get tweets from july to september.
The first method was to set up only the filter with dplyr, but that didn't work. Next, i had to set the since_id and max_id in the function get_timeline and n = Inf. 
In order to do that i took 2 tweets by the Matteo Salvini twitter account.

```{r, eval=FALSE}
since <- "1551558900247314435"
max <- "1573269167305854976"
cdx_tweet <- rtweet::get_timeline(retryonratelimit = T,
                                      user = list_italian_cdx,
                                      n = Inf,
                                      since_id = since,
                                      max_id = max,
                                      verbose = T, 
                                      parse = T,
) %>% 
  dplyr::filter(created_at > "2022-07-25" & created_at <="2022-09-24")

```

Thanks to this, I was able to download only the tweets of the period that interested me and I therefore also replied for the other coalitions.
The partial output was a dataframe for each coalition containing all the tweets. 
I then proceeded to export these tables in csv format which I saved in a new folder called "data".

```{r, eval=FALSE}
#export data
write.csv(cdx_tweet,"C:\\Users\\trava\\OneDrive\\Documenti\\Capstone_TravagliniSimone\\data\\cdx_tweet.csv", row.names=FALSE)
write.csv(csx_tweet,"C:\\Users\\trava\\OneDrive\\Documenti\\Capstone_TravagliniSimone\\data\\csx_tweet.csv", row.names=FALSE)
write.csv(m5s_tweet,"C:\\Users\\trava\\OneDrive\\Documenti\\Capstone_TravagliniSimone\\data\\m5s_tweet.csv", row.names=FALSE)
write.csv(terzopolo_tweet,"C:\\Users\\trava\\OneDrive\\Documenti\\Capstone_TravagliniSimone\\data\\terzopolo_tweet.csv", row.names=FALSE)
```

```{r, eval=FALSE}
#import data
cdx_tweet <- read.csv("C:\\Users\\trava\\OneDrive\\Documenti\\Capstone_TravagliniSimone\\data\\cdx_tweet.csv")
csx_tweet <- read.csv("C:\\Users\\trava\\OneDrive\\Documenti\\Capstone_TravagliniSimone\\data\\csx_tweet.csv")
m5s_tweet <- read.csv("C:\\Users\\trava\\OneDrive\\Documenti\\Capstone_TravagliniSimone\\data\\m5s_tweet.csv")
terzopolo_tweet <- read.csv("C:\\Users\\trava\\OneDrive\\Documenti\\Capstone_TravagliniSimone\\data\\terzopolo_tweet.csv")

```

## GET THE HASHTAGS

After analyzing the tables containing the tweets I decided that the best way to get hashtags was to use a regular expression. 
To achieve the goal I then proceeded to create 4 objects containing the lists of all tweets through the unlist function. 
After that i used the str_view_all and str_extract_all functions to see and export all the hashtags. finally I put them into objects called hashtag_cdx, hashtag_csx, hashtag_m5s and hashtag_terzopolo.

```{r, eval=FALSE}
list_cdx_tweet <- unlist(cdx_tweet$full_text)
list_cdx_tweet

list_csx_tweet <- unlist(csx_tweet$full_text)
list_csx_tweet

list_m5s_tweet <- unlist(m5s_tweet$full_text)
list_m5s_tweet

list_terzopolo_tweet <- unlist(terzopolo_tweet$full_text)
list_terzopolo_tweet

# open package
library(stringr)

#view if the regex is right
str_view_all(list_cdx_tweet,
             pattern = "#\\S+.")

#probably "#\\S+." is the right one
## cdx----
hashtag_cdx <- str_extract_all(list_cdx_tweet, pattern = "#\\S+.")  
## csx----
hashtag_csx <- str_extract_all(list_csx_tweet, pattern = "#\\S+.")
## m5s----
hashtag_m5s <- str_extract_all(list_m5s_tweet, pattern = "#\\S+.")
## terzopolo----
hashtag_terzopolo <- str_extract_all(list_terzopolo_tweet, pattern = "#\\S+.")  

```

After having taken all the hashtags of all the coalitions, the next step is that of the actual analysis. in order to analyze I decided to create wordclouds from the tables of the most used words as hashtags. 
These tables show, in ascending order, the hashtags most used by the coalitions during the electoral campaign period.

```{r, eval=FALSE}

library(wordcloud)

library(RColorBrewer)

library(wordcloud2)

## cdx----

#create a corpus

library(tm)


tweet_dx <- unlist(hashtag_cdx)
tweet_dx1 <- Corpus(VectorSource(tweet_dx))

#remove the symbol # and punctation
tweet_dx1 <- tweet_dx1 %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
tweet_dx1 <- tm_map(tweet_dx1, content_transformer(tolower))
tweet_dx1 <- tm_map(tweet_dx1, removeWords, stopwords("english"))

dtm <- TermDocumentMatrix(tweet_dx1) 
matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),decreasing=TRUE) 
df <- data.frame(word = names(words),freq=words)


## csx----

tweet_sx <- unlist(hashtag_csx)
tweet_sx1 <- Corpus(VectorSource(tweet_sx))

tweet_sx1 <- tweet_sx1 %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
tweet_sx1 <- tm_map(tweet_sx1, content_transformer(tolower))
tweet_sx1 <- tm_map(tweet_sx1, removeWords, stopwords("english"))

dtm2 <- TermDocumentMatrix(tweet_sx1) 
matrix2 <- as.matrix(dtm2) 
words2 <- sort(rowSums(matrix2),decreasing=TRUE) 
df2 <- data.frame(word = names(words2),freq=words2)

## m5s----
tweet_m5s <- unlist(hashtag_m5s)
tweet_m5s1 <- Corpus(VectorSource(tweet_m5s))

tweet_m5s1 <- tweet_m5s1 %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
tweet_m5s1 <- tm_map(tweet_m5s1, content_transformer(tolower))
tweet_m5s1 <- tm_map(tweet_m5s1, removeWords, stopwords("english"))

dtm3 <- TermDocumentMatrix(tweet_m5s1) 
matrix3 <- as.matrix(dtm3) 
words3 <- sort(rowSums(matrix3),decreasing=TRUE) 
df3 <- data.frame(word = names(words3),freq=words3)

### terzopolo-----
tweet_tp <- unlist(hashtag_terzopolo)
tweet_tp1 <- Corpus(VectorSource(tweet_tp))

tweet_tp1 <- tweet_tp1 %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
tweet_tp1 <- tm_map(tweet_tp1, content_transformer(tolower))
tweet_tp1 <- tm_map(tweet_tp1, removeWords, stopwords("english"))

dtm4 <- TermDocumentMatrix(tweet_tp1) 
matrix4 <- as.matrix(dtm4) 
words4 <- sort(rowSums(matrix),decreasing=TRUE) 
df4 <- data.frame(word = names(words4),freq=words4)

```


## OUTPUT ANALYSIS:

***LEFT COALITION:***

```{r, message=FALSE, warning=FALSE, eval=TRUE, echo=FALSE}
library(wordcloud2)
library(wordcloud)
library(RColorBrewer)

df2 <- read.csv("C:\\Users\\trava\\OneDrive\\Documenti\\Capstone_TravagliniSimone\\data\\top_hashtagcsx.csv")

wordcloud(words = df2$word, freq = df2$freq, min.freq = 10,
          max.words=Inf, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(10, "Dark2"),
          scale=c(2,0.60))
```

As we can see from the graphs above, the most used hashtags are green-left alliance and in any case those related to the environment and ecology (climate crisis, regasification terminals and ecological transition above all). however, there are also references to political opponents (especially Meloni, Salvini and Calenda).
Another fundamental point of the electoral campaign for the left was the right for homosexuals and the lgbt community. 
As seen in the wordcloud among the hashtags there are "egalitarian marriage" "lgbt" and "rights".
In the graph below instead we can see the 20 most used hashtags by the coalition:
The first one was "alleanzaverdisinistra", used more then 1000 times.

```{r,message=FALSE, warning=FALSE, eval=TRUE, echo=FALSE}
topcsx <- head(df2, 30)
barplot(topcsx$freq, names.arg = topcsx$word, las=2,
        col=c(3:8), 
        cex.axis=0.8, cex.names=0.7)


```



***RIGHT COALITION:***

```{r, message=FALSE, warning=FALSE, eval=TRUE, echo=FALSE}
library(wordcloud2)
library(wordcloud)
library(RColorBrewer)

df <- read.csv("C:\\Users\\trava\\OneDrive\\Documenti\\Capstone_TravagliniSimone\\data\\top_hashtagcDx.csv")

wordcloud(words = df$word, freq = df$freq, min.freq = 6,
          max.words=Inf, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(10, "Dark2"),
          scale=c(2,0.60))



```

The graphs show that the words most used by right-wing coalition politicians are those referring to voting for a reference party (lega, fdi and forza italia), but there are also hashtags referring to the main points of their electoral campaign (presidentialism, flat tax). 
One of the main ones is the hashtag #credo, launched precisely on the occasion of the elections by the leader of the Lega Matteo Salvini.
In the graph below instead we can see the 30 most used hashtags by the coalition:
the first was #credo, that was mentioned more than 500 times.

```{r, message=FALSE, warning=FALSE, echo=FALSE, eval=TRUE}
topcdx <- head(df, 30)
barplot(topcdx$freq, names.arg = topcdx$word, las=2,
        col=c(3:8), 
        cex.axis=0.8, cex.names=0.7)



```


***MOVIMENTO 5 STELLE ANALYSIS:***

```{r, message=FALSE, warning=FALSE, eval=TRUE, echo=FALSE}
library(wordcloud2)
library(wordcloud)
library(RColorBrewer)

df3 <- read.csv("C:\\Users\\trava\\OneDrive\\Documenti\\Capstone_TravagliniSimone\\data\\top_hashtagm5s.csv")

wordcloud(words = df3$word, freq = df3$freq, min.freq = 2,
          max.words=Inf, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(10, "Dark2"),
          scale=c(2,0.60))



```

As regards the analysis of the 5-star movement, I must say that I found a principal difficulty: the candidates of the movement (except for a few cases) did not use twitter much during the electoral campaign.
Although the list was large enough, I was able to export only 2760 tweets.
However we can say that, from the analysis of these hashtags, the one most used by far was "on the right side". 
Secondly, the others were those referring to basic income and the minimum wage, but also young people and expensive bills. 
Also in this case we find references to political opponents, first of all Meloni and Calenda.
As we can see from the plots here below, the hashtag "#dallapartegiusta" was vastly more used than the others, more than 6 times more than the second one:

```{r, message=FALSE, warning=FALSE, eval=TRUE, echo=FALSE}
topm5s <- head(df3, 30)
barplot(topm5s$freq, names.arg = topm5s$word, las=2,
        col=c(3:8), 
        cex.axis=0.8, cex.names=0.7)



```


***TERZO POLO ANALYSIS:***

```{r, message=FALSE, warning=FALSE, eval=TRUE, echo=FALSE}
library(wordcloud2)
library(wordcloud)
library(RColorBrewer)

df4 <- read.csv("C:\\Users\\trava\\OneDrive\\Documenti\\Capstone_TravagliniSimone\\data\\top_hashtagtp.csv")

wordcloud(words = df4$word, freq = df4$freq, min.freq = 6,
          max.words=Inf, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(10, "Dark2"),
          scale=c(2,0.60))



```

The slogan of the third pole coalition for the 2022 elections was "italia seriously", which was one of the most used hashtags in the period. 
In addition to this, the candidates expressed their views on infrastructure, health and justice reform. 
Also in this case we find references to political opponents, but in this circumstance, the candidates of the third pole referred above all to Berlusconi and Di Maio.

In the graph below instead we can see the 30 most used hashtags by the coalition:
the first was #italiasulserio, that was mentioned more than 1200 times. Another interesting thing is to find #Draghi as the third most used hashtag. Probably in reference to the fact that they were satisfied with Draghi's performance as head of government and wanted to continue their political action in that direction.


```{r, message=FALSE, warning=FALSE, eval=TRUE, echo=FALSE}
toptp <- head(df4, 30)
barplot(toptp$freq, names.arg = toptp$word, las=2,
        col=c(3:8), 
        cex.axis=0.8, cex.names=0.7)



```



## CONCLUSION

In conclusion, we can say that, all the coalitions have used the twitter channels to talk about their key points on the political agenda, or to refer to and attack their political opponents. from this analysis that only took into consideration the hashtags, I could only understand the topic in question, but not the message that was wanted to be sent.
During this electoral campaign, it has been seen that the parties have had a good deal of activity within their twitter accounts, despite the proximity between the day on which president Mattarella proclaimed the dissolution of the chambers and the elections.
The actual period was therefore only 2 months. 

One consideration that i feel I must make, however, is that in a historical period such as the one in which we live, it is possible to say that the classic electoral campaign no longer exists. 
I mean that anyone with a twitter profile or any other social media profile can see that most of the Italian political class appears in a perennial political campaign, with the aim of acquiring new voters and maintaining virtual relations with those already acquired.
That said, it is probable that even extending the search outside of this time period, we would have found the same topics among the tweets of the analysed politicians.
